---
title: "Billboard Lyrics"
author: "Vy Doan & Mia Nakamura"
date: "2024-04-30"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(mosaic)
library(BillboardLyrics)
library(tidytext)
```

This file describes the BillboardLyrics package.

The package is interesting as it offers the opportunity to conduct diverse analyses on Billboard's Top 100 Songs, covering the period from 1946 to 2015. Through it, we can delve into the evolution of popular music preferences over time, shedding light on the dynamic shifts in popular music over the decades. For instance, we can evaluate the success of individual artists or bands by monitoring their frequency on the Top 100 list, examining the longevity of their careers, and discerning the impact of specific songs on their overall achievements.

The BillboardLyrics package can be installed by running:

```
devtools::install_github("STAT231-S24/BillboardLyrics")
library(BillboardLyrics)
```

```{r}
packageVersion("BillboardLyrics")
glimpse(BillboardLyrics)
```

### **Limitations**

Within this package, certain song lyrics exhibit irregular spacing. For instance, in "Wooly Bully" by Sam the Sham and the Pharaohs, there's a spacing anomaly in the line "...sam the sham the pharaohs domingo..." where extra spaces surround "the pharaohs". Also, in "I Can't Help Myself Sugar Pie Honey Bunch", for some of the lyrics there is no spacing between some of the words: "i can docant help myself".

Number of irregular spelling occurrences: 

```{r}

odd <- BillboardLyrics |>
  mutate(
    odd_lyrics = str_detect(lyrics, pattern = "(hh|aa|eee|ii|ooo|uu|yy|sss)"),
  ) |>
  filter(odd_lyrics == TRUE) |>
  summarize(
    n = n()
  )
odd

```

If odd_lyrics = true, that means there is irregular spelling. There are 815 songs with irregular spelling. 

### **Sample Analyses**

```{r}
BillboardLyrics |>
  head(1) |>
  pull(lyrics)
```

#### Artists with the Most Billboard Appearances

```{r message = FALSE, warning = FALSE}
top_artists <- BillboardLyrics |>
  group_by(artist) |>
  summarise(billboard_appearances = n()) |>
  arrange(desc(billboard_appearances))

knitr::kable(head(top_artists))
```

Madonna dominated the Billboard Top 100 Charts from 1964 to 2015, making a remarkable 35 appearances—a feat unmatched by any other artist. In comparison, Elton John secured second place with a still impressive 29 appearances.


