---
title: "Billboard Lyrics"
author: "Vy Doan & Mia Nakamura"
date: "2024-04-12"
date-format: iso
format: gfm
editor: source
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(mosaic)
library(BillboardLyrics)
```

This file describes the BillboardLyrics package.

The package is interesting as it offers the opportunity to conduct diverse analyses on Billboard's Top 100 Songs, covering the period from 1946 to 2015. Through it, we can delve into the evolution of popular music preferences over time, shedding light on the dynamic shifts in popular music over the decades. For instance, we can evaluate the success of individual artists or bands by monitoring their frequency on the Top 100 list, examining the longevity of their careers, and discerning the impact of specific songs on their overall achievements.

The BillboardLyrics package can be installed by running:

```
devtools::install_github("STAT231-S24/BillboardLyrics")
library(BillboardLyrics)
```

```{r}
packageVersion("BillboardLyrics")
glimpse(BillboardLyrics)
```

**Limitation**

Within this package, certain song lyrics exhibit irregular spacing. For instance, in "Wooly Bully" by Sam the Sham and the Pharaohs, there's a spacing anomaly in the line "...sam the sham the pharaohs domingo..." where extra spaces surround "the pharaohs".

**Sample Analyses:**

```{r}
BillboardLyrics |>
  head(1) |>
  pull(lyrics)
```

```{r}
BillboardLyrics |>
  head(2) |>
  tail(1) |>
  pull(lyrics)
```

```{r}
BillboardLyrics |>
  head(4) |>
  tail(1) |>
  pull(lyrics)
```
